
```{r setup, include=FALSE}
#Setup the environment

rm(list=ls())
library(SnowballC)
library(tm)
library(ggplot2)
library(RColorBrewer)
library(wordcloud)
library(topicmodels)
library(data.table)
library(stringi)
library(syuzhet)
#library(qdap)
library(dplyr)
library(plyr)
library(grid)
library(gridExtra)
```

#####Read Twitter Data

```{r}
# Set directory and read data
tweets.df <- read.csv("mjemi.csv")
tweets.df$text <- as.character(tweets.df$text)
str(tweets.df)


#####Sentiment Analysis: understanding emotional valence in tweets using syuzhet

tweets.df$text <- iconv(enc2utf8(tweets.df$text),sub="byte")
mysentiment<-get_nrc_sentiment((tweets.df$text))


# Get the sentiment score for each emotion
mysentiment.positive =sum(mysentiment$positive)
mysentiment.anger =sum(mysentiment$anger)
mysentiment.anticipation =sum(mysentiment$anticipation)
mysentiment.disgust =sum(mysentiment$disgust)
mysentiment.fear =sum(mysentiment$fear)
mysentiment.joy =sum(mysentiment$joy)
mysentiment.sadness =sum(mysentiment$sadness)
mysentiment.surprise =sum(mysentiment$surprise)
mysentiment.trust =sum(mysentiment$trust)
mysentiment.negative =sum(mysentiment$negative)

# Create the bar chart
yAxis <- c(mysentiment.positive,
           + mysentiment.anger,
           + mysentiment.anticipation,
           + mysentiment.disgust,
           + mysentiment.fear,
           + mysentiment.joy,
           + mysentiment.sadness,
           + mysentiment.surprise,
           + mysentiment.trust,
           + mysentiment.negative)

xAxis <- c("Positive","Anger","Anticipation","Disgust","Fear","Joy","Sadness",
           "Surprise","Trust","Negative")
colors <- c("green","red","blue","orange","red","green","orange","blue","green","red")
yRange <- range(0,yAxis)
barplot(yAxis, names.arg = xAxis, 
        xlab = "Emotional valence", ylab = "Score", main = "Album sentiment", 
        sub = "MJ", col = colors, border = "black", xpd = F, ylim = yRange,
        axisnames = T, cex.axis = 0.8, cex.sub = 0.8, col.sub = "blue")

library(tidytext)
library(syuzhet)

words <- tweets.df %>% unnest_tokens(word,text)
sentiment <- words %>% inner_join(get_sentiments("laughron"),by="word")
sentiment %>% dplyr::count(word,sentiment,sort = TRUE) %>% group_by (sentiment) %>% top_n(n=10) %>% ungroup() %>% ggplot(aes(x=reorder(word,n),y=n,fill=sentiment)) + geom_col(show.legend = FALSE) + facet_wrap(~sentiment,scales="free") +  coord_flip()


mysentiment.anger
mysentiment.anticipation
mysentiment.disgust
mysentiment.fear
mysentiment.joy
mysentiment.negative
mysentiment.positive
mysentiment.sadness
mysentiment.surprise
mysentiment.trust


```


library(data.table)
fwrite(sentiment, "mjemi output.csv")



fwrite(prince_tidy, "distinct.csv")
#install.packages("devtools")
library(devtools)
#install_github("ndphillips/yarrr")
library(yarrr)

prince_tidy <- tweets.df %>%
  unnest_tokens(word, text) %>% #Break the lyrics into individual words
  filter(!nchar(word) < 3) %>% #Words like "ah" or "oo" used in music
  anti_join(stop_words) #Data provided by the tidytext package

glimpse(prince_tidy)
attach(prince_tidy)
prince_tidy$song <- as.character(prince_tidy$song)

word_summary <- prince_tidy %>%
  group_by(Year,song) %>%
  mutate(word_count = n_distinct(word)) %>%
  distinct() %>% #To obtain one record per song
  ungroup()

word_count = n_distinct(word)

pirateplot(formula =  word , #Formula
   data = word_summary, #Data frame
   xlab = NULL, ylab = "Song Distinct Word Count", #Axis labels
   main = "Lexical Diversity Per Year", #Plot title
   pal = "google", #Color scheme
   point.o = .2, #Points
   avg.line.o = 1, #Turn on the Average/Mean line
   theme = 0, #Theme
   point.pch = 16, #Point `pch` type
   point.cex = 1.5, #Point size
   jitter.val = .1, #Turn on jitter to see the songs better
   cex.lab = .9, cex.names = .7) #Axis label size

?pirateplot

